\huge A Usability Evaluation of Tor Launcher

### 2017-03-16 pets2017-paper/pets2017-paper.tex
dingledine2006anonymity as related work.

We do not know of any published usability studies of Tor Browser
since the introduction of Tor Launcher,
which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
Lee and Fifield ran an informal ``UX sprint''
for Tor Browser in 2015~\cite{uxsprint}, bringing together developers and users
to discover common usability problems.
They conducted detailed walkthroughs with five participants,
in a precursor to the present work.
There are some studies that evaluated earlier forms of web browsing over Tor,
without a particular focus on configuration.
Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
investigated ``stop-points''
in the installation and use of Tor Browser,
places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.
Fabian et~al.~\cite{fabian2010privately}, in 2010,
estimated how much Tor's added latency harms usability
(considered separately from user interface concerns).
They measured the latency of requests to common websites with and without Tor,
and mapped the latencies to compute an expected ``cancelation rate,''
the fraction of users who would have given up waiting for a request to complete.
They estimated a median cancelation rate of 88\% for Tor, compared to 14\% for direct requests.
% \cite{dingledine2009performance}
In 2007, Clark et~al.~\cite{clark2007usability}
used cognitive walkthroughs to evaluate four
methods of web browsing over Tor
(all of which have since been superseded by Tor Browser and Tor Launcher).
Evaluating each method against a set of guidelines,
they found that none were fully satisfactory,
though the ones that used automatic configuration did better.

>>>>

We do not know of any published usability studies of Tor Browser
since the introduction of Tor Launcher,
which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
Lee and Fifield ran an informal ``UX sprint''
for Tor Browser in 2015~\cite{uxsprint}, bringing together developers and users
to discover common usability problems.
They conducted detailed walkthroughs with five participants,
in a precursor to the present work.
There are some studies that evaluated earlier forms of web browsing over Tor,
without a particular focus on configuration.
Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
investigated ``stop-points''
in the installation and use of Tor Browser,
places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.
Fabian et~al.~\cite{fabian2010privately}, in 2010,
estimated how much Tor's added latency harms usability
(considered separately from user interface concerns).
They measured the latency of requests to common websites with and without Tor,
and mapped the latencies to compute an expected ``cancelation rate,''
the fraction of users who would have given up waiting for a request to complete.
They estimated a median cancelation rate of 88\% for Tor, compared to 14\% for direct requests.
In 2007, Clark et~al.~\cite{clark2007usability}
used cognitive walkthroughs to evaluate four
methods of web browsing over Tor
(all of which have since been superseded by Tor Browser and Tor Launcher).
Evaluating each method against a set of guidelines,
they found that none were fully satisfactory,
though the ones that used automatic configuration did better.
In 2006, Dingledine and Mathewson~\cite{dingledine2006anonymity}
emphasized that anonymizing networks, by their nature,
require lots of users, so usability is an even greater concern
than with other security systems.
They considered a case study of the ease of installing Tor,
at a time when technically inexperienced users were just beginning to use it.
